article title

### 2022-08-25 article.tex
Refactor sections for clarity
Fix equation numbering

\newpage
\listoffigures

@@

\begin{flalign}
    \text{distance to nearest specification} & = \frac{\text{nearest specification} - \text{location statistic}}{\text{dispersion statistic}}&& \\
                                             & = \frac{\text{min}\,(\overline{X} - \text{LSL}\,, \text{USL} - \overline{X})}{s}&&
\end{flalign}
\myequations{Distance to nearest specification}

@@

\begin{flalign}
A=\begin{pmatrix}
1 &0 &4 &-1 \\
0 &1 &-3 &1 \\
0 &0 &0 &1
\end{pmatrix}&&
\end{flalign}

\begin{flalign}
A = \begin{bmatrix}
1 &0 &4 &-1\\
0 &1 &-3 &1 \\
0 &0 &0 &1
\end{bmatrix}&&
\end{flalign}

@@

Here is a request to fill in \gls{dependent_variable} and \glspl{dependent_variable}.

@@

@@

\newpage
\section{Acknowledgements}\label{sec:acknowledgements}

\section{Supporting information}\label{sec:supporting_information}

Add files, data, and other supporting information, and where it can be obtained.
all

>>>>

\newpage
\section*{Acknowledgements}\label{sec:acknowledgements}

\section*{Supporting information}\label{sec:supporting_information}

Add files, data, and other supporting information, and where it can be obtained.

\listoffigures

@@

\begin{flalign}
    \text{distance to nearest spec} = \frac{\text{nearest spec} - \text{location statistic}}{\text{dispersion statistic}}  = \frac{\text{min}\,(\overline{X} - \text{LSL}\,, \text{USL} - \overline{X})}{s} &&
\end{flalign}
\myequations{Distance to nearest specification}

@@

\begin{flalign}
A=\begin{pmatrix}
1 &0 &4 &-1 \\
0 &1 &-3 &1 \\
0 &0 &0 &1
\end{pmatrix}&&
\end{flalign}
\myequations{Matrix p format}

\begin{flalign}
A = \begin{bmatrix}
1 &0 &4 &-1\\
0 &1 &-3 &1 \\
0 &0 &0 &1
\end{bmatrix}&&
\end{flalign}
\myequations{Matrix b format}

@@

Here is a request to fill in \gls{dependentvariable} and \glspl{dependentvariable}.

@@

\gls{fixedeffectsmodel}

\gls{randomeffectsmodel}

\gls{expectedmeansquares}

\gls{mixedeffectsmodel}

@@
